Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-06 articles/cycle/alps-cycle.tex
Remove calving methods.

      Ice deformation
      follows temperature and water-content dependent creep
      (Sect.~\ref{sec:icedyn}). Default parameter values are given in
      Table~\ref{tab:params}. Basal sliding follows
      a~pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Ice shelf calving is simulated using an ice thickness threshold and
      principle components of the strain rate tensor
      (Sect.~\ref{sec:calving}). Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbed
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}). A~sensitivity study
      to some of the most influential ice rheology (Sect~\ref{sec:icedyn})
      and basal sliding (Sect.~\ref{sec:sliding}) parameters is performed
      (Table~\ref{tab:sens_params}).

@@

\subsection{Ice shelf calving}
\label{sec:calving}

      Ice shelf calving is computed using a~double criterion. First,
      a~physically-realistic calving flux is computed based on eigenvalues
      of the horizontal strain rate tensor \citep{Winkelmann.etal.2011,
      Levermann.etal.2012}. This allows floating ice to advance in confined
      embayments, but prevents the formation of extensive ice shelves in the
      open ocean. Second, floating ice thinner than 50\,\unit{m} is
      systematically calved off. A~subgrid scheme by
      \citet{Albrecht.etal.2011} allows for a~continuous migration of the
      calving front. This formulation of calving has been applied to the
      Antarctic ice sheet and has shown to produce a~realistic calving front
      positon for many of the present-day ice shelves
      \citep{Martin.etal.2011}.

>>>>

      Ice deformation
      follows temperature and water-content dependent creep
      (Sect.~\ref{sec:icedyn}). Default parameter values are given in
      Table~\ref{tab:params}. Basal sliding follows
      a~pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbed
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}). A~sensitivity study
      to some of the most influential ice rheology (Sect~\ref{sec:icedyn})
      and basal sliding (Sect.~\ref{sec:sliding}) parameters is performed
      (Table~\ref{tab:sens_params}).

@@
